\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-27 papers/jfp/7-experience.tex
Clean up the section on relationship to Shake tasks

\begin{minted}[xleftmargin=10pt]{haskell}
data Action k v = Finished v
                | Depends v (v -> Action)
\end{minted}

In some sense this is the ``free'' version of the \hs{Task Monad} -- the two types form an isomorphism. Similary, \Make tasks were described as equivalent to

\begin{minted}[xleftmargin=10pt]{haskell}
data Rule k v = Rule {depends :: [k], action :: [v] -> v}
\end{minted}

Once again, this type is isomorphism to \hs{Task Applicative}. By describing these types using \hs{Task} we are able to pinpoint the differences (\hs{Monad} vs \hs{Applicative}) and use existing literature to prove what is and isn't possible.

>>>>

\begin{minted}[xleftmargin=10pt]{haskell}
data Action k v r = Finished r
                  | Depends v (v -> Action k r)
\end{minted}

In some sense this is the ``free'' version of the \hs{Task Monad} \cite{free-applicatives} -- the two types form an isomorphism. The originally paper uses concrete types \hs{Key} and \hs{Value}, we generalise these types to \hs{k} and \hs{v}, and also add \hs{r} so that \hs{Action k v} can be an instance of \hs{Monad}. We can write that \hs{Monad} instance, and use it to write conversion functions to/from our \hs{Task} type:

\begin{minted}[xleftmargin=10pt]{haskell}
instance Monad (Action k v) where
    return = Finished
    Finished x >>= f = f x
    Depends ds op >>= f = Depends ds $ \v -> f =<< op v

toAction :: Task Monad k v -> Action k v v
toAction (Task run) = run $ \k -> Depends k Finished

fromAction :: Action k v v -> Task Monad k v
fromAction x = Task $ \fetch -> f fetch x
    where f fetch (Finished v) = return v
          f fetch (Depends d op) = f fetch . op =<< fetch d
\end{minted}

Similary, \Make tasks were described as equivalent to

\begin{minted}[xleftmargin=10pt]{haskell}
data Rule k v r = Rule {depends :: [k], action :: [v] -> r}
\end{minted}

Once again, this type is isomorphic to \hs{Task Applicative}, and we can define a similar \hs{Applicative} instance and conversion functions. By describing these types using \hs{Task} we are able to pinpoint the differences (\hs{Monad} vs \hs{Applicative}) and use existing literature to prove what is and isn't possible.
